Details matter: Similar host galaxies can harbor different merging compact binary populations

### 2016-07-12 paper/paper.tex
Prepping organization

@@

\appendix

>>>>

\editremark{recheck numbers: we are tweaking things, and Zsun is seemingly inconsistent in the two approaches }
 Our two galaxies have extremely similar star formation histories and metallicity evolution, particularly at late
 times.  
However, at early times, the exciting galaxy forms stars for $\simeq 2\unit{Gyr}$ at a lower characteristic metallicity
($Z\simeq 0.8 10^{-3}$) compared
to the borinng galaxy ($Z\simeq 2\times 10^{-3}$).  In this reigme, the formation efficiency $\lambda$ and sensitive volume $V$
can depend sensitively on mass; for example, for binary black holes, the ratio of  $(\lambda V)_{boring}/(\lambda
V)_{exciting} \simeq 7$.
% 1e-3:  V = 276, lambda= 400   
% 2e-3:  V= 152.657625157, lambda = 100
% so the ratio should be a factor of about 7x higher due to this region.
Therefore, though only a fraction \textbf{XXX} of all star formation occurs in this epoch, by this order of magnitude
argument, the overall number of
present-day coalescing binary black holes in our two galaxies is expected to differ by as much as a factor of \textbf{YYY (=2?)}.  
%
Using the concrete phenomenological calculations described above, we in fact find
$r_{D,boring}/r_{D,exciting}=\textbf{ZZZ}$.

The origin of the differenc

@@
